---
title: "ANCOVA test for triagem (avaliação triagem)"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Teste ANCOVA para determinar se houve diferenças significativas
         na avaliação triagem (medido usando pre- e pos-testes).
         
         ANCOVA test to determine whether there were significant differences
         in triagem evaluation (measured using pre- and post-tests).
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         This file is  generate using Shiny-Statistic app (https://github.com/geiser/rshinystatistics)
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---

Teste ANCOVA para determinar se houve diferenças significativas
na avaliação triagem (medido usando pre- e pos-testes).
         
ANCOVA test to determine whether there were significant differences
in triagem evaluation (measured using pre- and post-tests).

```{r setup, include=FALSE}
# Install and Load Packages

if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(shiny)
library(esquisse)
library(scales)
library(knitr)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(rshinystatistics)
```

```{r, include=FALSE, purl=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE)
defaultW <- getOption("warn")
options(warn = -1)
```

```{r, include=FALSE}

# Setting Initial Variables

dat <- readxl::read_excel("../data/data.xlsx", sheet = "summary")
dat <- dat[!is.na(dat[["pre_score.triagem"]]) & !is.na(dat[["pos_score.triagem"]]),]
dat$idade <- sapply(dat$idade, FUN = function(v) {
  if (!is.null(v) && !is.na(v)) return(paste0(v,"y")) else return(NA)
})
dat$intervention <- factor(dat$intervention, c("Controle","Stari","WordGen","Stari and WordGen"))
dat$genero <- factor(dat$genero, c("F","M"))
dat$zona.escola <- factor(dat$zona.escola, c("Urbana","Rural"))
dat$zona.participante <- factor(dat$zona.participante, c("Urbana","Rural"))

dat.long <- readxl::read_excel("../data/data.xlsx", sheet = "summary.long")
dat.long <- dat.long[!is.na(dat.long[["score.triagem"]]),]

dat.long$time <- factor(dat.long$time, c("pre","pos"))
dat.long$idade <- sapply(dat.long$idade, FUN = function(v) {
  if (!is.null(v) && !is.na(v)) return(paste0(v,"y")) else return(NA)
})
dat.long$intervention <- factor(dat.long$intervention, c("Controle","Stari","WordGen","Stari and WordGen"))
dat.long$genero <- factor(dat.long$genero, c("F","M"))
dat.long$zona.escola <- factor(dat.long$zona.escola, c("Urbana","Rural"))
dat.long$zona.participante <- factor(dat.long$zona.participante, c("Urbana","Rural"))


fatores <- c("genero","idade","zona.escola","zona.participante","escola","monitor",
             "monitor.genero","monitor.formacao","monitor.experiencia","monitor.titulacao")
lfatores <- as.list(fatores)
names(lfatores) <- fatores


color <- list()
color[["prepost"]] = c("#ffee65","#ffb55a")
color[["intervention"]] = c("#a4a2a8","#fd7f6f","#1984c5","#5ad45a")
color[["genero"]] = c("#FF007F","#4D4DFF")
color[["zona.escola"]] = c("#AA00FF","#00CCCC")
color[["zona.participante"]] = c("#AA00FF","#00CCCC")

for (f in c("intervention",fatores)) {
  if (is.null(color[[f]])) 
    color[[f]] <- distinctColorPalette(length(unique(dat[[f]])))
}
for (f in c(fatores)) {
  if (is.null(color[[paste0("intervention:",f)]])) 
    color[[paste0("intervention:",f)]] <- distinctColorPalette(length(unique(dat[["intervention"]]))*length(unique(dat[[f]])))
}

lfatores1 <- as.list(c("intervention", fatores))
names(lfatores1) <- c("intervention", fatores)
```

# Descriptive Statistics of Initial Data

## Baseado nos acertos (score) da prova

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score.triagem","pre_score.triagem"), c("intervention", "genero")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score.triagem","pre_score.triagem"), c("intervention", "escola")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score.triagem","pre_score.triagem"), c("intervention", "zona.escola")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score.triagem","pre_score.triagem"), c("intervention", "zona.participante")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score.triagem","pre_score.triagem"), c("intervention", "monitor")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

## Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score_tri.triagem","pre_score_tri.triagem"), c("intervention", "genero")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```


```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score_tri.triagem","pre_score_tri.triagem"), c("intervention", "escola")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score_tri.triagem","pre_score_tri.triagem"), c("intervention", "zona.escola")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score_tri.triagem","pre_score_tri.triagem"), c("intervention", "zona.participante")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

```{r, include=FALSE}
(df <- get.descriptives(dat, c("pos_score_tri.triagem","pre_score_tri.triagem"), c("intervention", "monitor")))
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

# Checking of Assumptions

## Identify and dealing with outliers (performing treatment of outliers)

```{r, echo=FALSE, include=FALSE}
(df <- rstatix::identify_outliers(
  group_by(dat[,c("id","intervention","genero","escola","zona.escola", "zona.participante","pos_score.triagem","pre_score.triagem")], intervention, genero, escola, zona.escola, zona.participante),
  "pos_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, echo=FALSE, include=FALSE}
(df <- rstatix::identify_outliers(
  group_by(dat[,c("id","intervention","genero","escola","zona.escola", "zona.participante","pos_score_tri.triagem","pre_score_tri.triagem")], intervention, genero, escola, zona.escola, zona.participante),
  "pos_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

## Assumption: Normality distribution of data

**Note**: To satisfy normality assumption no one outlier need to be removed

### Para fatores de: **intervention:genero**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","genero"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","genero"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:idade**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","idade"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","idade"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:zona.escola**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","zona.escola"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","zona.escola"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:zona.participante**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","zona.participante"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","zona.participante"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:escola**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","escola"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","escola"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:monitor**

```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score.triagem", c("intervention","monitor"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, echo=FALSE, include=FALSE}
(df <- normality.test.by.residual(dat, "pos_score_tri.triagem", c("intervention","monitor"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


## Assumption: Homogeneity of data distribution

*Note*: Can be applied parametric tests, all data satisfied homogeneity tests

### Para fatores de: **intervention:genero**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["genero"]]),], "pos_score.triagem", c("intervention","genero"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["genero"]]),], "pos_score_tri.triagem", c("intervention","genero"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:idade**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["idade"]]),], "pos_score.triagem", c("intervention","idade"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:zona.escola**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["zona.escola"]]),], "pos_score.triagem", c("intervention","zona.escola"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["zona.escola"]]),], "pos_score_tri.triagem", c("intervention","zona.escola"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:zona.participante**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["zona.participante"]]),], "pos_score.triagem", c("intervention","zona.participante"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["zona.participante"]]),], "pos_score_tri.triagem", c("intervention","zona.participante"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:escola**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["escola"]]),], "pos_score.triagem", c("intervention","escola"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["escola"]]),], "pos_score_tri.triagem", c("intervention","escola"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

### Para fatores de: **intervention:monitor**

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["monitor"]]),], "pos_score.triagem", c("intervention","monitor"), c(), "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

```{r, echo=FALSE, include=FALSE}
(df <- homogeneity.test(dat[!is.na(dat[["monitor"]]),], "pos_score_tri.triagem", c("intervention","monitor"), c(), "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

# Computation of ANCOVA test and Pairwise Comparison

## ANCOVA test

### ANCOVA test usando acertos (pontuação - score) da prova

```{r, echo=FALSE, include=FALSE}
aovs1.score <- lapply(lfatores1, FUN = function(x) {
  aov = ancova.test(dat[!is.na(dat[[x]]),], "pos_score.triagem", x, "pre_score.triagem", 2, "ges")$pos_score.triagem
  cbind(formula=rep(paste0("pos_score.triagem ~ pre_score.triagem + ",x),nrow(aov)), aov)
})

aovs2.score <- lapply(lfatores, FUN = function(x) {
  aov = ancova.test(dat[!is.na(dat[[x]]),], "pos_score.triagem", c("intervention", x), "pre_score.triagem", 2, "ges")$pos_score.triagem
  cbind(formula=rep(paste0("pos_score.triagem ~ pre_score.triagem + intervention"," * ",x),nrow(aov)), aov)
})

aov1.score <- do.call(rbind, aovs1.score)
row.names(aov1.score) <- c()

aov2.score <- do.call(rbind, aovs2.score)
row.names(aov2.score) <- c()

aov.score <- rbind(aov1.score, aov2.score)
aov.score <- aov.score[!duplicated(aov.score$Effect),]
row.names(aov.score) <- c()
```

```{r, echo=FALSE, purl=FALSE}
df <- round.pval(aov.score)
kable(df[,c("Effect","DFn","DFd","SSn","SSd","F","p","ges","p<.05")], digits=3)
```

### ANCOVA test usando as estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova

```{r, echo=FALSE, include=FALSE}
aovs1.tri <- lapply(lfatores1, FUN = function(x) {
  aov = ancova.test(dat[!is.na(dat[[x]]),], "pos_score_tri.triagem", x, "pre_score_tri.triagem", 2, "ges")$pos_score_tri.triagem
  cbind(formula=rep(paste0("pos_score_tri.triagem ~ pre_score_tri.triagem + ",x),nrow(aov)), aov)
})

aovs2.tri <- lapply(lfatores, FUN = function(x) {
  aov = ancova.test(dat[!is.na(dat[[x]]),], "pos_score_tri.triagem", c("intervention", x), "pre_score_tri.triagem", 2, "ges")$pos_score_tri.triagem
  cbind(formula=rep(paste0("pos_score_tri.triagem ~ pre_score_tri.triagem + intervention"," * ",x),nrow(aov)), aov)
})

aov1.tri <- do.call(rbind, aovs1.tri)
row.names(aov1.tri) <- c()

aov2.tri <- do.call(rbind, aovs2.tri)
row.names(aov2.tri) <- c()

aov.tri <- rbind(aov1.tri, aov2.tri)
aov.tri <- aov.tri[!duplicated(aov.tri$Effect),]
row.names(aov.tri) <- c()
```

```{r, echo=FALSE, purl=FALSE}
df <- round.pval(aov.tri)
kable(df[,c("Effect","DFn","DFd","SSn","SSd","F","p","ges","p<.05")], digits=3)
```


## Pairwise comparisons for one factor

### factor: **intervention** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "intervention", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "intervention", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "intervention", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "intervention"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "intervention", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "intervention", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "intervention", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "intervention", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention"]],
  subtitle = which(aov.tri$Effect == "intervention"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "intervention", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factor: **genero** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["genero"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("genero"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "genero", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("genero"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","genero"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","genero"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "genero", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["genero"]] + ggplot2::scale_color_manual(values = color[["genero"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "genero", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["genero"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["genero"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "genero", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["genero"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["genero"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("genero"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "genero", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("genero"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","genero"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","genero"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "genero", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["genero"]] + ggplot2::scale_color_manual(values = color[["genero"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "genero", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["genero"]],
  subtitle = which(aov.tri$Effect == "genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "genero", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factor: **idade** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["idade"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("idade"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "idade", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("idade"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["idade"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","idade"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","idade"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("idade","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "idade", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "idade"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["idade"]] + ggplot2::scale_color_manual(values = color[["idade"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "idade", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["idade"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "idade"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["idade"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "idade", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["idade"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["idade"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("idade"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "idade", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("idade"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["idade"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","idade"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","idade"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("idade","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "idade", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "idade"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["idade"]] + ggplot2::scale_color_manual(values = color[["idade"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "idade", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["idade"]],
  subtitle = which(aov.tri$Effect == "idade"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["idade"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "idade", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["idade"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factor: **zona.escola** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["zona.escola"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("zona.escola"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "zona.escola", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("zona.escola"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["zona.escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","zona.escola"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","zona.escola"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "zona.escola", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "zona.escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.escola"]] + ggplot2::scale_color_manual(values = color[["zona.escola"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "zona.escola", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["zona.escola"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "zona.escola"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.escola"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "zona.escola", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.escola"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["zona.escola"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("zona.escola"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "zona.escola", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("zona.escola"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["zona.escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","zona.escola"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","zona.escola"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "zona.escola", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "zona.escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.escola"]] + ggplot2::scale_color_manual(values = color[["zona.escola"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "zona.escola", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["zona.escola"]],
  subtitle = which(aov.tri$Effect == "zona.escola"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "zona.escola", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```



### factor: **zona.participante** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["zona.participante"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("zona.participante"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "zona.participante", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("zona.participante"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["zona.participante"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","zona.participante"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","zona.participante"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.participante","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "zona.participante", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "zona.participante"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.participante"]] + ggplot2::scale_color_manual(values = color[["zona.participante"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "zona.participante", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["zona.participante"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "zona.participante"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.participante"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "zona.participante", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.participante"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["zona.participante"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("zona.participante"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "zona.participante", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("zona.participante"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["zona.participante"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","zona.participante"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","zona.participante"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.participante","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "zona.participante", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "zona.participante"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.participante"]] + ggplot2::scale_color_manual(values = color[["zona.participante"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "zona.participante", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["zona.participante"]],
  subtitle = which(aov.tri$Effect == "zona.participante"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.participante"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "zona.participante", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["zona.participante"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factor: **escola** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["escola"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("escola"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "escola", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("escola"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","escola"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","escola"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "escola", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["escola"]] + ggplot2::scale_color_manual(values = color[["escola"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "escola", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["escola"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "escola"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["escola"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "escola", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["escola"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["escola"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("escola"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "escola", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("escola"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","escola"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","escola"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "escola", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["escola"]] + ggplot2::scale_color_manual(values = color[["escola"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "escola", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["escola"]],
  subtitle = which(aov.tri$Effect == "escola"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "escola", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factor: **monitor** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score.triagem", c("monitor"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "monitor", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("monitor"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","monitor"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","monitor"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "monitor", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "monitor"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor"]] + ggplot2::scale_color_manual(values = color[["monitor"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "monitor", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["monitor"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "monitor"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["monitor"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "monitor", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("monitor"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "monitor", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("monitor"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","monitor"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","monitor"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "monitor", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "monitor"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor"]] + ggplot2::scale_color_manual(values = color[["monitor"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "monitor", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["monitor"]],
  subtitle = which(aov.tri$Effect == "monitor"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["monitor"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "monitor", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["monitor"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factor: **monitor.genero** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.genero"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score.triagem", c("monitor.genero"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "monitor.genero", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("monitor.genero"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.genero"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","monitor.genero"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","monitor.genero"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "monitor.genero", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "monitor.genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor.genero"]] + ggplot2::scale_color_manual(values = color[["monitor.genero"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "monitor.genero", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["monitor.genero"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "monitor.genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.genero"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "monitor.genero", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.genero"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.genero"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("monitor.genero"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "monitor.genero", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("monitor.genero"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.genero"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","monitor.genero"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","monitor.genero"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "monitor.genero", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "monitor.genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor.genero"]] + ggplot2::scale_color_manual(values = color[["monitor.genero"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "monitor.genero", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["monitor.genero"]],
  subtitle = which(aov.tri$Effect == "monitor.genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "monitor.genero", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factor: **monitor.formacao** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.formacao"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score.triagem", c("monitor.formacao"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "monitor.formacao", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("monitor.formacao"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.formacao"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","monitor.formacao"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","monitor.formacao"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.formacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "monitor.formacao", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "monitor.formacao"))
```

```{r, dpi=300, fig.width=21, fig.height=7}
plots[["monitor.formacao"]] + ggplot2::scale_color_manual(values = color[["monitor.formacao"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "monitor.formacao", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["monitor.formacao"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "monitor.formacao"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["monitor.formacao"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "monitor.formacao", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["monitor.formacao"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.formacao"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("monitor.formacao"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "monitor.formacao", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("monitor.formacao"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.formacao"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","monitor.formacao"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","monitor.formacao"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.formacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "monitor.formacao", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "monitor.formacao"))
```

```{r, dpi=300, fig.width=21, fig.height=7}
plots[["monitor.formacao"]] + ggplot2::scale_color_manual(values = color[["monitor.formacao"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "monitor.formacao", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["monitor.formacao"]],
  subtitle = which(aov.tri$Effect == "monitor.formacao"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["monitor.formacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "monitor.formacao", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["monitor.formacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factor: **monitor.titulacao** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.titulacao"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score.triagem", c("monitor.titulacao"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "monitor.titulacao", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("monitor.titulacao"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.titulacao"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","monitor.titulacao"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","monitor.titulacao"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.titulacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "monitor.titulacao", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "monitor.titulacao"))
```

```{r, dpi=300, fig.width=10, fig.height=7}
plots[["monitor.titulacao"]] + ggplot2::scale_color_manual(values = color[["monitor.titulacao"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "monitor.titulacao", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["monitor.titulacao"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "monitor.titulacao"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["monitor.titulacao"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "monitor.titulacao", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["monitor.titulacao"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.titulacao"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("monitor.titulacao"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "monitor.titulacao", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("monitor.titulacao"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.titulacao"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","monitor.titulacao"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","monitor.titulacao"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.titulacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "monitor.titulacao", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "monitor.titulacao"))
```

```{r, dpi=300, fig.width=8, fig.height=7}
plots[["monitor.titulacao"]] + ggplot2::scale_color_manual(values = color[["monitor.titulacao"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "monitor.titulacao", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["monitor.titulacao"]],
  subtitle = which(aov.tri$Effect == "monitor.titulacao"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.titulacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "monitor.titulacao", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.titulacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factor: **monitor.experiencia** 

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.experiencia"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score.triagem", c("monitor.experiencia"))

pwc = ancova.pwc(pdat, "pos_score.triagem", "monitor.experiencia", "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("monitor.experiencia"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.experiencia"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","monitor.experiencia"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","monitor.experiencia"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.experiencia","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score.triagem", "monitor.experiencia", aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "monitor.experiencia"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor.experiencia"]] + ggplot2::scale_color_manual(values = color[["monitor.experiencia"]])
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat, "pos_score.triagem", "monitor.experiencia", aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["monitor.experiencia"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "monitor.experiencia"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.experiencia"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- oneWayAncovaBarPlots(
  pdat.long, "score.triagem", "monitor.experiencia", aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=7, fig.height=6}
plots[["monitor.experiencia"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["monitor.experiencia"]]) & dat$monitor.count == 1,]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("monitor.experiencia"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", "monitor.experiencia", "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("monitor.experiencia"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c(".y.","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["monitor.experiencia"]]) & dat.long$monitor.count == 1,]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","monitor.experiencia"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","monitor.experiencia"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.experiencia","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- oneWayAncovaPlots(pdat, "pos_score_tri.triagem", "monitor.experiencia", aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "monitor.experiencia"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["monitor.experiencia"]] + ggplot2::scale_color_manual(values = color[["monitor.experiencia"]])
```

```{r}
plots <- oneWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", "monitor.experiencia", aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["monitor.experiencia"]],
  subtitle = which(aov.tri$Effect == "monitor.experiencia"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.experiencia"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- oneWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", "monitor.experiencia", aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["monitor.experiencia"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

## Pairwise comparisons for two factor

### factores: **intervention:genero**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["genero"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","genero"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","genero"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","genero"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","genero","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","genero"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","genero"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","genero"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["genero"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["genero"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","genero"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:genero"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "intervention:genero"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:genero"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","genero"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:genero"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["genero"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","genero"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","genero"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","genero"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","genero","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","genero"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","genero"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","genero"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["genero"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["genero"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","genero"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:genero"]],
  subtitle = which(aov.tri$Effect == "intervention:genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","genero"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```




### factores: **intervention:idade**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["idade"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","idade"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","idade"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","idade"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","idade","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["idade"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","idade"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","idade"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("idade","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","idade"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:idade"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["idade"]]$data)))
  plots[["idade"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["idade"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","idade"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:idade"]], step.increase = 0.8,
  subtitle = which(aov.score$Effect == "intervention:idade"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:idade"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","idade"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:idade"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["idade"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","idade"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","idade"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","idade"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","idade","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["idade"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","idade"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","idade"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","idade","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","idade"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.05, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:idade"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["idade"]]$data)))
  plots[["idade"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["idade"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","idade"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:idade"]],
  subtitle = which(aov.tri$Effect == "intervention:idade"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["intervention:idade"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","idade"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=15, fig.height=6}
plots[["intervention:idade"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factores: **intervention:zona.escola**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["zona.escola"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","zona.escola"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","zona.escola"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","zona.escola"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","zona.escola","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["zona.escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","zona.escola"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","zona.escola"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","zona.escola"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:zona.escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.escola"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["zona.escola"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","zona.escola"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:zona.escola"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "intervention:zona.escola"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:zona.escola"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","zona.escola"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:zona.escola"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["zona.escola"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","zona.escola"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","zona.escola"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","zona.escola"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","zona.escola","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["zona.escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","zona.escola"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","zona.escola"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","zona.escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","zona.escola"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:zona.escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.escola"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["zona.escola"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","zona.escola"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:zona.escola"]],
  subtitle = which(aov.tri$Effect == "intervention:zona.escola"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:zona.escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","zona.escola"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:zona.escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factores: **intervention:zona.participante**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["zona.participante"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","zona.participante"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","zona.participante"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","zona.participante"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","zona.participante","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["zona.participante"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","zona.participante"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","zona.participante"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("zona.participante","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","zona.participante"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:zona.participante"))
```

```{r, dpi=300, fig.width=10, fig.height=7}
plots[["zona.participante"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["zona.participante"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","zona.participante"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:zona.participante"]], step.increase = 0.7,
  subtitle = which(aov.score$Effect == "intervention:zona.participante"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:zona.participante"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","zona.participante"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:zona.participante"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["zona.participante"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","zona.participante"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","zona.participante"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","zona.participante"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","zona.participante","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["zona.participante"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","zona.participante"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","zona.participante"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","zona.participante","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","zona.participante"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.05, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:zona.participante"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["zona.participante"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["zona.participante"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","zona.participante"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:zona.participante"]],
  subtitle = which(aov.tri$Effect == "intervention:zona.participante"))
```

```{r, dpi=300, fig.width=10, fig.height=6}
plots[["intervention:zona.participante"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","zona.participante"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:zona.participante"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factores: **intervention:escola**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["escola"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","escola"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","escola"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","escola"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","escola","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","escola"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","escola"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","escola"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["escola"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["escola"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","escola"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:escola"]], step.increase = 0.75,
  subtitle = which(aov.score$Effect == "intervention:escola"))
```

```{r, dpi=300, fig.width=14, fig.height=6}
plots[["intervention:escola"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","escola"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=26, fig.height=6}
plots[["intervention:escola"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[!is.na(dat[["intervention"]]) & !is.na(dat[["escola"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","escola"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","escola"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","escola"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","escola","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[!is.na(dat.long[["intervention"]]) & !is.na(dat.long[["escola"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","escola"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","escola"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","escola","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","escola"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:escola"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["escola"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["escola"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","escola"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:escola"]],
  subtitle = which(aov.tri$Effect == "intervention:escola"))
```

```{r, dpi=300, fig.width=14, fig.height=6}
plots[["intervention:escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","escola"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:escola"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factores: **intervention:monitor**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","monitor"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","monitor"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","monitor"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","monitor"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","monitor"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","monitor"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:monitor"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor"]]$data)))
  plots[["monitor"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","monitor"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:monitor"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "intervention:monitor"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","monitor"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=16, fig.height=6}
plots[["intervention:monitor"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","monitor"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","monitor"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","monitor"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","monitor"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","monitor"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","monitor","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","monitor"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:monitor"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor"]]$data)))
  plots[["monitor"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","monitor"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:monitor"]],
  subtitle = which(aov.tri$Effect == "intervention:monitor"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","monitor"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=15, fig.height=6}
plots[["intervention:monitor"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factores: **intervention:monitor.genero**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.genero"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","monitor.genero"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","monitor.genero"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","monitor.genero"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.genero","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","monitor.genero"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","monitor.genero"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","monitor.genero"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:monitor.genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.genero"]]$data)))
  plots[["monitor.genero"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.genero"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","monitor.genero"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:monitor.genero"]], step.increase = 0.75,
  subtitle = which(aov.score$Effect == "intervention:monitor.genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:monitor.genero"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","monitor.genero"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:monitor.genero"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.genero"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","monitor.genero"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","monitor.genero"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","monitor.genero"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.genero","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.genero"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","monitor.genero"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","monitor.genero"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","monitor.genero","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","monitor.genero"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.05, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:monitor.genero"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.genero"]]$data)))
  plots[["monitor.genero"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.genero"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","monitor.genero"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:monitor.genero"]],
  subtitle = which(aov.tri$Effect == "intervention:monitor.genero"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:monitor.genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","monitor.genero"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.genero"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```


### factores: **intervention:monitor.formacao**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.formacao"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","monitor.formacao"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","monitor.formacao"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","monitor.formacao"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.formacao","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.formacao"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","monitor.formacao"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","monitor.formacao"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.formacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","monitor.formacao"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:monitor.formacao"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.formacao"]]$data)))
  plots[["monitor.formacao"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.formacao"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","monitor.formacao"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:monitor.formacao"]], step.increase = 0.5,
  subtitle = which(aov.score$Effect == "intervention:monitor.formacao"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.formacao"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","monitor.formacao"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=30, fig.height=6}
plots[["intervention:monitor.formacao"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.formacao"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","monitor.formacao"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","monitor.formacao"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","monitor.formacao"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.formacao","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.formacao"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","monitor.formacao"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","monitor.formacao"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","monitor.formacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","monitor.formacao"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:monitor.formacao"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.formacao"]]$data)))
  plots[["monitor.formacao"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.formacao"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","monitor.formacao"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:monitor.formacao"]],
  subtitle = which(aov.tri$Effect == "intervention:monitor.formacao"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.formacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","monitor.formacao"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=28, fig.height=6}
plots[["intervention:monitor.formacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factores: **intervention:monitor.titulacao**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.titulacao"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","monitor.titulacao"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","monitor.titulacao"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","monitor.titulacao"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.titulacao","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.titulacao"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","monitor.titulacao"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","monitor.titulacao"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.titulacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","monitor.titulacao"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:monitor.titulacao"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.titulacao"]]$data)))
  plots[["monitor.titulacao"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=10, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.titulacao"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","monitor.titulacao"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:monitor.titulacao"]], step.increase = 0.75,
  subtitle = which(aov.score$Effect == "intervention:monitor.titulacao"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.titulacao"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","monitor.titulacao"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=20, fig.height=6}
plots[["intervention:monitor.titulacao"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.titulacao"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","monitor.titulacao"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","monitor.titulacao"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","monitor.titulacao"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.titulacao","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.titulacao"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","monitor.titulacao"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","monitor.titulacao"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","monitor.titulacao","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","monitor.titulacao"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:monitor.titulacao"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.titulacao"]]$data)))
  plots[["monitor.titulacao"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=10, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.titulacao"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","monitor.titulacao"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:monitor.titulacao"]],
  subtitle = which(aov.tri$Effect == "intervention:monitor.titulacao"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:monitor.titulacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","monitor.titulacao"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.titulacao"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```

### factores: **intervention:monitor.experiencia**

#### Baseado nos acertos (score) da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.experiencia"]]),]
pdat = remove_group_data(pdat, "pos_score.triagem", c("intervention","monitor.experiencia"))

pwc = ancova.pwc(pdat, "pos_score.triagem", c("intervention","monitor.experiencia"), "pre_score.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score.triagem", c("intervention","monitor.experiencia"), "apa-format", covar = "pre_score.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.experiencia","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.experiencia"]]),]
pdat.long = remove_group_data(pdat.long, "score.triagem", c("time","intervention","monitor.experiencia"))

pwc.long = anova.pwc(pdat.long, "score.triagem", c("time","intervention","monitor.experiencia"))
pwc.long = pwc.long$score.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("monitor.experiencia","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score.triagem", c("intervention","monitor.experiencia"), aov.score, pwc$pos_score.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.025, p.label="p.adj",
                           subtitle = which(aov.score$Effect == "intervention:monitor.experiencia"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.experiencia"]]$data)))
  plots[["monitor.experiencia"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.experiencia"]])
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat, "pos_score.triagem", c("intervention","monitor.experiencia"), aov.score, pwc$pos_score.triagem, covar = "pre_score.triagem",
  theme = "classic", color = color[["intervention:monitor.experiencia"]], step.increase = 0.75,
  subtitle = which(aov.score$Effect == "intervention:monitor.experiencia"))
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.experiencia"]] + ggplot2::ylab("pontuação (triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```

```{r}
plots <- twoWayAncovaBarPlots(
  pdat.long, "score.triagem", c("intervention","monitor.experiencia"), aov.score, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.experiencia"]] + ggplot2::ylab("pontuação (triagem)")
```


#### Baseado nas estimativas da aprendizagem (theta - traço latente) mediante TRI aplicado as respostas da prova


```{r, include=FALSE}
pdat = dat[dat$monitor.count == 1 & !is.na(dat[["intervention"]]) & !is.na(dat[["monitor.experiencia"]]),]
pdat = remove_group_data(pdat, "pos_score_tri.triagem", c("intervention","monitor.experiencia"))

pwc = ancova.pwc(pdat, "pos_score_tri.triagem", c("intervention","monitor.experiencia"), "pre_score_tri.triagem", pwc.covar=T)

(apa <- get.ancova.emmeans.with.ds(pwc, pdat, "pos_score_tri.triagem", c("intervention","monitor.experiencia"), "apa-format", covar = "pre_score_tri.triagem"))
```

```{r, echo=FALSE, purl=FALSE}
kable(apa, digits = 3)
```

```{r, include=FALSE}
pdf <- get.ancova.pwc.table(pwc, only.sig = F)
(pdf <- pdf[!is.na(pdf$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf <- round.pval(pdf)
kable(pdf[,c("intervention","monitor.experiencia","group1","group2","estimate","conf.low",
             "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```


```{r, include=FALSE}
pdat.long = dat.long[dat.long$monitor.count == 1 & !is.na(dat.long[["intervention"]]) & !is.na(dat.long[["monitor.experiencia"]]),]
pdat.long = remove_group_data(pdat.long, "score.tri.triagem", c("time","intervention","monitor.experiencia"))

pwc.long = anova.pwc(pdat.long, "score.tri.triagem", c("time","intervention","monitor.experiencia"))
pwc.long = pwc.long$score.tri.triagem$time
(pdf.long <- pwc.long[!is.na(pwc.long$p.adj),])
```

```{r, echo=FALSE, purl=FALSE}
pdf.long <- round.pval(pdf.long)
kable(pdf.long[,c("intervention","monitor.experiencia","group1","group2","estimate","conf.low",
                  "conf.high","se","statistic","p","p.adj","p.adj.signif")], digits = 3)
```

```{r}
plots <- twoWayAncovaPlots(pdat, "pos_score_tri.triagem", c("intervention","monitor.experiencia"), aov.tri, pwc$pos_score_tri.triagem,
                           addParam = c("jitter"), font.label.size=14,
                           step.increase=0.25, p.label="p.adj",
                           subtitle = which(aov.tri$Effect == "intervention:monitor.experiencia"))
```

```{r, dpi=300, fig.width=7, fig.height=7}
if (!is.null(nrow(plots[["monitor.experiencia"]]$data)))
  plots[["monitor.experiencia"]] + ggplot2::scale_color_manual(values = color[["intervention"]])
```

```{r, dpi=300, fig.width=10, fig.height=7}
if (!is.null(nrow(plots[["intervention"]]$data)))
  plots[["intervention"]] + ggplot2::scale_color_manual(values = color[["monitor.experiencia"]])
```



```{r}
plots <- twoWayAncovaBoxPlots(
  pdat, "pos_score_tri.triagem", c("intervention","monitor.experiencia"), aov.tri, pwc$pos_score_tri.triagem, covar = "pre_score_tri.triagem",
  theme = "classic", color = color[["intervention:monitor.experiencia"]],
  subtitle = which(aov.tri$Effect == "intervention:monitor.experiencia"))
```

```{r, dpi=300, fig.width=8, fig.height=6}
plots[["intervention:monitor.experiencia"]] + ggplot2::ylab("theta (aprendizagem de triagem)") + ggplot2::scale_x_discrete(labels=c('pre', 'pos'))
```


```{r}
plots <- twoWayAncovaBoxPlots(
  pdat.long, "score.tri.triagem", c("intervention","monitor.experiencia"), aov.tri, pwc.long, pre.post = "time",
  theme = "classic", color = color$prepost)
```

```{r, dpi=300, fig.width=12, fig.height=6}
plots[["intervention:monitor.experiencia"]] + ggplot2::ylab("theta (aprendizagem de triagem)")
```



