---
title: "ANCOVA test for {{ label }} (engajamento no {{ label }})"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Teste ANCOVA para determinar se houve diferenças significativas
         em referência ao engajamento no {{ label }} (medido como estado de fluxo).
         
         ANCOVA test to determine whether there were significant differences
         in reference to engagement in {{ label }} (measured as flow state).
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         This file is  generate using Shiny-Statistic app (https://github.com/geiser/rshinystatistics)
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---

**NOTE**

 - Teste ANCOVA para determinar se houve diferenças significativas
em referência ao engajamento no {{ label }} (medido como estado de fluxo).
 - ANCOVA test to determine whether there were significant differences
in reference to engagement in {{ label }} (measured as flow state).

```{r setup, include=FALSE}
# Install and Load Packages

if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(shiny)
library(esquisse)
library(scales)
library(knitr)
library(rmarkdown)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(rshinystatistics)
```

```{r, include=FALSE, purl=FALSE}
options(knitr.kable.NA = '')
opts_chunk$set(echo = FALSE)
defaultW <- getOption("warn")
options(warn = -1)
```

```{r, include=FALSE}
# Setting Initial Variables
escolas <- readxl::read_excel("{{ file.path }}", sheet = "escolas")
monitor <- readxl::read_excel("{{ file.path }}", sheet = "monitores")

dat <- readxl::read_excel("{{ file.path }}", sheet = "{{ sheet }}")
dat <- merge(dat, escolas, by.x = "escola", by.y = "id", all.x = T, all.y = F)
dat <- merge(dat, monitor, by.x = "monitor", by.y = "id", all.x = T, all.y = F)
dat[["monitor"]] <- sapply(1:nrow(dat), FUN = function(i) {
  if (dat$monitor.count[i] == 1) dat$monitor[i] else NA
})

dat <- dat[!is.na(dat[["{{ column.dfs }}"]]) & !is.na(dat[["{{ column.fss }}"]]),]
dat$idade <- sapply(dat$idade, FUN = function(v) {
  if (!is.null(v) && !is.na(v)) return(paste0(v,"y")) else return(NA)
})

dat$grupo <- as.vector(sapply(dat$grupo, FUN = function(x) {
  if (x == "Controle") "Controle" else "{{ exp.lab }}" 
}))
dat$grupo <- factor(dat$grupo, c("Controle","{{ exp.lab }}"))
dat$genero <- factor(dat$genero, c("F","M"))
dat$zona.escola <- factor(dat$zona.escola, c("Urbana","Rural"))
dat$zona.participante <- factor(dat$zona.participante, c("Urbana","Rural"))

dat.long <- tidyr::gather(dat, time, {{ column.flow }}, {{ column.dfs }}, {{ column.fss }})
dat.long <- dat.long[!is.na(dat.long[["{{ column.flow }}"]]),]
dat.long$time[dat.long$time=="{{ column.dfs }}"] <- "pre"
dat.long$time[dat.long$time=="{{ column.fss }}"] <- "pos"
dat.long$time <- factor(dat.long$time, c("pre","pos"))

fatores2 <- c({{ paste0(paste0('"', fatores ,'"'), collapse = ",") }})
lfatores2 <- as.list(fatores2)
names(lfatores2) <- fatores2

fatores1 <- c("grupo", fatores2)
lfatores1 <- as.list(fatores1)
names(lfatores1) <- fatores1

fatores3 <- c({{ paste0(paste0('"', info.monitor ,'"'), collapse = ",") }})
lfatores3 <- as.list(fatores3)
names(lfatores3) <- fatores3

lfatores <- c(lfatores1, lfatores3)

color <- list()
color[["prepost"]] = c("#ffee65","#f28e2B")
color[["grupo"]] = c("#bcbd22","{{ exp.color }}")
color[["genero"]] = c("#FF007F","#4D4DFF")
color[["zona.escola"]] = c("#AA00FF","#00CCCC")
color[["zona.participante"]] = c("#AA00FF","#00CCCC")

for (f in c("grupo", names(lfatores))) {
  if (is.null(color[[f]])) 
    color[[f]] <- distinctColorPalette(length(unique(dat[[f]])))
}
for (f in c(fatores2)) {
  if (is.null(color[[paste0("grupo:",f)]])) 
    color[[paste0("grupo:",f)]] <- distinctColorPalette(length(unique(dat[["grupo"]]))*length(unique(dat[[f]])))
}
```

# Descriptive Statistics of Initial Data

```{r, include=FALSE}
df <- do.call(plyr::rbind.fill, lapply(lfatores2, FUN = function(f) {
  get.descriptives(dat, c("{{ column.fss }}","{{ column.dfs }}"), c("grupo", f))
}))
(df <- df[,c(fatores1,"variable", colnames(df)[!colnames(df) %in% c(fatores1,"variable")])])
```

```{r, echo=FALSE, purl=FALSE}
kable(df, digits = 3)
```

# Checking of Assumptions

## Assumption: Normality distribution of data

```{r, echo=FALSE, include=FALSE}
(df <- do.call(plyr::rbind.fill, lapply(lfatores2, FUN = function(f) {
  normality.test.by.residual(dat, "{{ column.fss }}", c("grupo", f), c(), "{{ column.dfs }}")
})))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

## Assumption: Homogeneity of data distribution

```{r, echo=FALSE, include=FALSE}
(df <- do.call(plyr::rbind.fill, lapply(lfatores2, FUN = function(f) {
  homogeneity.test(dat[!is.na(dat[[f]]),], "{{ column.fss }}", c("grupo", f), c(), "{{ column.dfs }}")
})))
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```

# Computation of ANCOVA test and Pairwise Comparison

## ANCOVA tests for one factor

```{r, echo=FALSE, include=FALSE}
aovs1 <- lapply(lfatores1, FUN = function(x) {
  aov = ancova.test(dat[!is.na(dat[[x]]),], "{{ column.fss }}",
                    x, "{{ column.dfs }}", 2, "ges")${{ column.fss }}
  cbind(formula=rep(paste0("{{ column.fss }} ~ {{ column.dfs }} + ",x), nrow(aov)), aov)
})

aov1 <- do.call(rbind, aovs1)
row.names(aov1) <- c()
(aov1 <- aov1[!duplicated(aov1$Effect),])
```

```{r, echo=FALSE, purl=FALSE}
df <- round.pval(aov1)
kable(df[,c("Effect","DFn","DFd","SSn","SSd","F","p","ges","p<.05")], digits=3)
```

## ANCOVA tests for two factors

```{r, echo=FALSE, include=FALSE}
aovs2 <- lapply(lfatores2, FUN = function(x) {
  tdat <- dat[!is.na(dat[[x]]),]
  if (length(unique(tdat$grupo)) >= 2 &&  length(unique(tdat[[x]])) >= 2) {
    aov = ancova.test(tdat, "{{ column.fss }}", c("grupo", x), "{{ column.dfs }}", 2, "ges")${{ column.fss }}
    return(cbind(formula=rep(paste0("{{ column.fss }} ~ {{ column.dfs }} + grupo"," * ",x), nrow(aov)), aov))  
  }
})

aov2 <- do.call(rbind, aovs2)
row.names(aov2) <- c()
(aov2 <- aov2[!duplicated(aov2$Effect) & !aov2$Effect %in% fatores1,])
```

```{r, echo=FALSE, purl=FALSE}
df <- round.pval(aov2)
kable(df[,c("Effect","DFn","DFd","SSn","SSd","F","p","ges","p<.05")], digits=3)
```

## ANCOVA tests for grupo="{{ exp.lab }}"

```{r, echo=FALSE, include=FALSE}
aovs3 <- lapply(lfatores3, FUN = function(x) {
  tdat <- dat[!is.na(dat[[x]]),]
  if (length(unique(tdat[[x]])) >= 2) {
    aov = ancova.test(tdat, "{{ column.fss }}", x,
                      "{{ column.dfs }}", 2, "ges")${{ column.fss }}
    return(cbind(formula=rep(
      paste0("{{ column.fss }} ~ {{ column.dfs }} + grupo=`Experimental`"," * ", x),
      nrow(aov)), aov))  
  }
})

aov3 <- do.call(rbind, aovs3)
row.names(aov3) <- c()
(aov3 <- aov3[!duplicated(aov3$Effect),])
```

```{r, echo=FALSE, purl=FALSE}
df <- round.pval(aov3)
kable(df[,c("Effect","DFn","DFd","SSn","SSd","F","p","ges","p<.05")], digits=3)
```


