---
title: "ANCOVA in {{ label.en }} ({{ label.pt }})"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Teste ANCOVA para determinar se houve diferenças significativas
         na {{ label.pt }} (medido usando pre- e pos-testes).
         
         ANCOVA test to determine whether there were significant differences
         in {{ label.en }} (measured using pre- and post-tests).
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         This file is  generate using Shiny-Statistic app (https://github.com/geiser/rshinystatistics)
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---

**NOTE**

 - Teste ANCOVA para determinar se houve diferenças significativas
no {{ label.pt }} (medido usando pre- e pos-testes).
 - ANCOVA test to determine whether there were significant differences
in {{ label.en }} (measured using pre- and post-tests).

```{r setup, include=FALSE}
# Install and Load Packages

if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(shiny)
library(esquisse)
library(scales)
library(knitr)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(dplyr)

library(rshinystatistics)
```

```{r, include=FALSE, purl=FALSE}
library(knitr)
options(knitr.kable.NA = '')
opts_chunk$set(echo = FALSE)
defaultW <- getOption("warn")
options(warn = -1)
```

```{r, include=FALSE}
# Setting Initial Variables
fatores2 <- c({{ paste0(paste0('"', fatores ,'"'), collapse = ",") }})
lfatores2 <- as.list(fatores2)
names(lfatores2) <- fatores2

fatores1 <- c("grupo", fatores2)
lfatores1 <- as.list(fatores1)
names(lfatores1) <- fatores1

fatores3 <- c({{ paste0(paste0('"', info.monitor ,'"'), collapse = ",") }})
lfatores3 <- as.list(fatores3)
names(lfatores3) <- fatores3

lfatores <- c(lfatores1, lfatores3)

# ..

escolas <- readxl::read_excel("{{ file.path }}", sheet = "escolas")
monitor <- readxl::read_excel("{{ file.path }}", sheet = "monitores")
monitor <- monitor[,c("id",fatores3[-1])]

  
dat <- list()
dat.long <- list()
for (dv in c({{ paste0(paste0('"', names(sub),'"'), collapse=",") }})) {
  df <- readxl::read_excel("{{ file.path }}", sheet = "{{ sheet }}.wide")
  df$idade <- sapply(df$idade, FUN = function(v) {
    if (!is.null(v) && !is.na(v)) return(paste0(v,"y")) else return(NA)
  })
  df <- merge(df, escolas, by.x = "escola", by.y = "id", all.x = T, all.y = F)
  df <- merge(df, monitor, by.x = "monitor", by.y = "id", all.x = T, all.y = F)
  df[["monitor"]] <- sapply(1:nrow(df), FUN = function(i) {
    if (df$monitor.count[i] == 1) df$monitor[i] else NA
  })
  df$grupo <- factor(df$grupo, c("Controle","Experimental"))
  df$genero <- factor(df$genero, c("F","M"))
  df$zona.escola <- factor(df$zona.escola, c("Urbana","Rural"))
  df$zona.participante <- factor(df$zona.participante, c("Urbana","Rural"))
  
  dat[[dv]] <- df[!is.na(df[[paste0(dv,".pre")]]) & !is.na(df[[paste0(dv,".pos")]]),]
  
  df <- readxl::read_excel("{{ file.path }}", sheet = "{{ sheet }}.long")
  df$idade <- sapply(df$idade, FUN = function(v) {
    if (!is.null(v) && !is.na(v)) return(paste0(v,"y")) else return(NA)
  })
  df <- merge(df, escolas, by.x = "escola", by.y = "id", all.x = T, all.y = F)
  df <- merge(df, monitor, by.x = "monitor", by.y = "id", all.x = T, all.y = F)
  df[["monitor"]] <- sapply(1:nrow(df), FUN = function(i) {
    if (df$monitor.count[i] == 1) df$monitor[i] else NA
  })
  df$time <- factor(df$time, c("pre","pos"))
  df$grupo <- factor(df$grupo, c("Controle","Experimental"))
  df$genero <- factor(df$genero, c("F","M"))
  df$zona.escola <- factor(df$zona.escola, c("Urbana","Rural"))
  df$zona.participante <- factor(df$zona.participante, c("Urbana","Rural"))
  
  dat.long[[dv]] <- df[!is.na(df[[dv]]),]
}

color <- list()
for (dv in c({{ paste0(paste0('"', names(sub),'"'), collapse=",") }})) {
  color[[dv]] <- list()
  color[[dv]][["prepost"]] = c("#ffee65","#f28e2B")
  color[[dv]][["grupo"]] = c("#bcbd22","{{ exp.color }}")
  color[[dv]][["genero"]] = c("#FF007F","#4D4DFF")
  color[[dv]][["zona.escola"]] = c("#AA00FF","#00CCCC")
  color[[dv]][["zona.participante"]] = c("#AA00FF","#00CCCC")
}

for (f in c("grupo", names(lfatores))) {
  for (dv in c({{ paste0(paste0('"', names(sub),'"'), collapse=",") }})) {
    if (is.null(color[[dv]][[f]])) 
      color[[dv]][[f]] <- distinctColorPalette(length(unique(dat[[dv]][[f]])))
  }
}
for (f in c(fatores2)) {
  for (dv in c({{ paste0(paste0('"', names(sub),'"'), collapse=",") }})) {
    if (is.null(color[[paste0("grupo:",f)]])) 
      color[[paste0("grupo:",f)]] <- distinctColorPalette(length(unique(dat[[dv]][["grupo"]]))*length(unique(dat[[dv]][[f]])))
  }
}
```

# Descriptive Statistics of Initial Data

{{ descriptive }}

# Checking of Assumptions

## Assumption: Normality distribution

{{ normality }}

## Assumption: Homogeneity

{{ homogeneity }}

# Computation of ANCOVA test and Pairwise Comparison

```{r, echo=FALSE, include=FALSE}
aov1 <- list()
aov2 <- list()
aov3 <- list()
```

## ANCOVA tests for one factor

{{ ancova.one }}

## ANCOVA tests for two factors

{{ ancova.two }}

## ANCOVA tests for grupo="Experimental"

{{ ancova.exp }}



